---
title: "CW_1606"
author: "Mindiya De Zoysa"
date: "2024-04-06"
output:
  word_document: default
  pdf_document: default
---

##Question 1:
###(a)
```{r}
bag1 <- c(rep(5, 5), rep(10, 3))
bag2 <- c(rep(15, 2), rep(20, 4))

draw1 <- sample(bag1, 1)
draw2 <- sample(bag2, 1)

sum <- draw1 + draw2

print(paste("Possible values of X:", sum))
```

##(b)
```{r}
bag1 <- c(rep(5, 5), rep(10, 3))
bag2 <- c(rep(15, 2), rep(20, 4))

sums <- vector()

for (ball1 in bag1) {
  for (ball2 in bag2) {
    sum <- ball1 + ball2
    sums <- c(sums, sum)
  }
}

freq_table <- table(sums)

total_outcomes <- length(bag1) * length(bag2)

pmf <- freq_table / total_outcomes

print("Value of X | Probability")
for (i in 1:length(pmf)) {
  print(paste(names(pmf)[i], "|", pmf[i]))
}
```

##(c)
```{r}
values <- c(20, 25, 30)
probabilities <- c(5/24, 13/24, 1/4)

expected_value <- sum(values * probabilities)
cat("Expected Value (E(X)):", expected_value, "\n")

expected_value_squared <- sum((values^2) * probabilities)

variance <- expected_value_squared - expected_value^2
cat("Variance (Var(X)):", variance, "\n")
```

##(d)
```{r}
X_values <- c(20, 25, 30)
X_probabilities <- c(5/24, 13/24, 1/4)

Y_values <- (2 * X_values) - 3

data <- data.frame(X = X_values, Y = Y_values, Probability = X_probabilities)

print(data)
```

##(e)
```{r}
prob_X <- c(5/24, 13/24, 1/4)

X_values <- c(20, 25, 30)

Y_values <- (2*X_values) - 3

pmf_Y <- prob_X

cdf_Y <- cumsum(pmf_Y)

cat("\nCDF of Y:\n")
for (i in 1:length(Y_values)) {
  cat("Y <", Y_values[i], "with probability", cdf_Y[i], "\n")
}
cat("Y <", Y_values[length(Y_values)], "with probability 1\n")
```

##(f)
```{r}
Y_values <- c(37, 47, 57)

cdf_Y <- c(5/24, 18/24, 1)

index_Y_37 <- which(Y_values == 37)

P_Y_37 <- cdf_Y[index_Y_37] - ifelse(index_Y_37 > 1, cdf_Y[index_Y_37 - 1], 0)

```
\newpage

##Question 2:
###(a)
```{r}
x <- rnorm(n = 500, mean = 36, sd = 8)
hist(x,freq = FALSE, breaks = 10, col = "skyblue", border = "black", 
     main = "Histogram of Random Sample", xlab = "Values", ylab = "Frequency" )
```

##(b)
```{r}
x <- rnorm(n = 500, mean = 36, sd = 8)
hist(x,freq = FALSE, breaks = 10, col = "skyblue", border = "black", 
     main = "Histogram of Random Sample", xlab = "Values", ylab = "Frequency" )
curve(dnorm(x,mean(x),sd(x)),add = TRUE, col = "red", lwd = 2)
```

##(c)
##So in this the histogram hasn't shiftted a lot to one side that means not hard to left or right but it is in the middle and also the density curve is in the middle. 

\newpage

##Question 3:
###(a)
```{r}
library(ggplot2)

data <- data.frame(
  X = c(2, 2.5, 3, 3.5, 4, 4.5, 5, 5.5, 6),
  Y = c(6, 7.25, 8, 9.0625, 10, 11.0625, 12.25, 13.5625, 15)
)

ggplot(data, aes(x = Y, y = X)) +
  geom_point(size = 3) +
  geom_smooth(method = "lm", se = FALSE) +
  labs(title = "Plot of Y versus X",
       x = "Y",
       y = "X")
```

##(b)
```{r}
library(ggplot2)

data <- data.frame(
  X = c(2, 2.5, 3, 3.5, 4, 4.5, 5, 5.5, 6),
  Y = c(6, 7.25, 8, 9.0625, 10, 11.0625, 12.25, 13.5625, 15)
)

correlation_coefficient <- cor(data$Y, data$X)

print(paste("Correlation coefficient (r):", correlation_coefficient))
```

##(c)
###The Correlation coefficient value is 0.997 so that means it is close to 1. In this case it is a strong correlationa and also the values are more accurate that is why it is getting a answer which is close to 1.


##(d)
```{r}
last_six_data <- tail(data, 6)

correlation_coefficient_last_six <- cor(last_six_data$Y, last_six_data$X)

print(paste("Correlation coefficient (R_x,y) for the last six pairs of data:", correlation_coefficient_last_six))

correlation_coefficient_all <- cor(data$Y, data$X)

print(paste("Correlation coefficient (R_x,y) for all data points:", correlation_coefficient_all))
```
###So the value has changed a bit after the 5th decimal point. But yet the correlation is strong as it is very much close to 1.


##(e)
```{r}
data$X1 <- 2 * data$X - 1
data$X2 <- data$X^2

cor_xy <- cor(data$Y, data$X)
cor_x1y <- cor(data$Y, data$X1)
cor_x2y <- cor(data$Y, data$X2)

print(paste("Correlation coefficient (r_x,y):", cor_xy))
print(paste("Correlation coefficient (r_x1,y):", cor_x1y))
print(paste("Correlation coefficient (r_x2,y):", cor_x2y))
```
##The (r_x,y) = (r_x1,y) as they borth holds the same value but yet the other answer (r_x2,y) is way more different that the answer what we are getting before.


\newpage

##Question 4:
###(a)
```{r}
data(mtcars)

head(mtcars, 10)
```

##(b)
```{r}
data(mtcars)

summary(mtcars$mpg)
summary(mtcars$hp)
```

##(c)
```{r}
data(mtcars)

plot(mtcars$mpg, mtcars$hp, 
     xlab = "Miles Per Gallon (mpg)", 
     ylab = "Horsepower (hp)",
     main = "Scatter Plot of mpg vs hp")
```

##(d)
```{r}
data(mtcars)

model <- lm(mpg ~ hp, data = mtcars)

summary(model)

fitted_values <- predict(model)

plot(mtcars$hp, mtcars$mpg, 
     xlab = "Horsepower (hp)", 
     ylab = "Miles Per Gallon (mpg)",
     main = "Linear Regression: mpg vs hp")

abline(model, col = "red")

legend("topright", legend = paste("Regression Line: ", round(coef(model)[1], 2), " + ", round(coef(model)[2], 2), " * hp"),
       col = "red", lty = 1)
```

##(e)
```{r}
data(mtcars)

model <- lm(mpg ~ hp, data = mtcars)

intercept <- coef(model)[1]
slope <- coef(model)[2]

fitted_equation <- paste("mpg =", round(intercept, 2), "+", round(slope, 2), "* hp")

cat("Fitted Equation:", fitted_equation, "\n")

change_in_mpg <- slope
cat("Change in mpg when hp increases by one unit:", round(change_in_mpg, 2), "units\n")
```

##(f)
```{r}
data(mtcars)

model <- lm(mpg ~ hp, data = mtcars)

plot(mtcars$hp, resid(model), 
     xlab = "Horsepower (hp)", 
     ylab = "Residuals",
     main = "Residual Plot: Residuals vs. Horsepower")

abline(model, col = "red")
```

##(g)
```{r}
data(mtcars)

model <- lm(mpg ~ hp, data = mtcars)

hp_value <- 110
predicted_mpg <- predict(model, newdata = data.frame(hp = hp_value))

cat("Predicted mpg for a car with horsepower of 110:", predicted_mpg, "\n")
```


\newpage

##Question 5:
###Part-A
###(a)
```{r}
mean <- 5.50
standard_deviation <- 1.20

percentile_90 <- qnorm(0.90, mean, standard_deviation)

print(percentile_90)
```

##(b)
```{r}
mean <- 5.50
standard_deviation <- 1.20

percentile_25 <- qnorm(0.25, mean, standard_deviation)

print(percentile_25)
```

##(c)
```{r}
mean <- 5.50

median_value <- mean

print(median_value)
```

##(d)
```{r}
mean <- 5.50
standard_deviation <- 1.20
threshold <- 7.00

cumulative_probability_up_to_7 <- pnorm(threshold, mean, standard_deviation)

percentage_more_than_7 <- 1 - cumulative_probability_up_to_7

percentage_more_than_7 <- percentage_more_than_7 * 100

print(percentage_more_than_7)
```


\newpage

##Question 5:
###Part-b
###(a)
###Binomial Distribution
###n = 50, p = 0.05

##(b)
```{r}
size <- 50
prob <- 0.05
q <- 2

prob_fewer_than_3 <- pbinom(q, size, prob)

print(prob_fewer_than_3)
```

##(c)
```{r}
mean_X <- 50 * 0.05
var_X <- 50 * 0.05 * (1 - 0.05)

cat("Mean of X:", mean_X, "\n")
cat("Variance of X:", var_X, "\n")
```

##(d)
###Binomial distribution. Because still theere are only two options in infected part. Also the sample sized is only fixed n=200, p=0.02



\newpage

##Question 6:
###(a)
```{r}
N <- 20000
my_boootstrap <- numeric(N)
exam_scores <- c(82, 88, 75, 94, 90, 85, 78, 91, 86, 89, 92, 80, 87, 79, 84, 77, 83, 81, 76, 93, 88, 85, 89, 90, 82, 86, 75, 91, 79, 84, 78, 95, 88, 87, 93, 86, 82, 89, 90, 80)

mean(exam_scores)
```

###(b)
```{r}
N <- 20000
my_boootstrap <- numeric(N)
exam_scores <- c(82, 88, 75, 94, 90, 85, 78, 91, 86, 89, 92, 80, 87, 79, 84, 77, 83, 81, 76, 93, 88, 85, 89, 90, 82, 86, 75, 91, 79, 84, 78, 95, 88, 87, 93, 86, 82, 89, 90, 80)

mean(exam_scores)

for (i in 1:N) {
  s=sample(exam_scores,10,replace = T)
  my_boootstrap[i]=mean(s)
}

hist(my_boootstrap, main = "Sampling Distribution of Sample Mean", xlab = "Sample Mean", ylab = "Frequency", col = "skyblue", border = "white")
```

##(c)
```{r}
quantile (my_boootstrap, c(0.90))
```

##(d)
```{r}
qqnorm(my_boootstrap)
qqline(my_boootstrap)
```